# Introduction {#sec:intro}

This is a R Markdown template for thesis' at the Department of Statistics, LMU.

You are not obligated to work with this template (despite we highly recommend it), but for the final submission you need 
to provide a repository with a similar structure and running code.

To create html output of this intro chapter click the **Knit** button. To create html or pdf (see drop down menu) output of 
the complete thesis template click the **Knit** button in `00_thesis.Rmd`.

## R Markdown and Bookdown

The template builds on R Markdown and its extension Bookdown.  

> Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R
Markdown see <http://rmarkdown.rstudio.com>.
>
> When you click the **Knit** button a document will be generated that includes both content as well as the output of any
embedded R code chunks within the document. 
>
> --- R Studio

For a quick overview see the [R Markdown cheat sheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/rmarkdown.pdf) 
and for the details the [R Markdown](https://bookdown.org/yihui/rmarkdown) and [Bookdown](https://bookdown.org/yihui/bookdown/) 
(esp. [Ch. 2.2](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html) and [Ch. 3.4](https://bookdown.org/yihui/bookdown/a-single-document.html)) books.


## Including R (or other) Code

You can embed R code 

- directly in a Rmd file, e.g.

```{r direct, echo = FALSE}
summary(cars)
```

- by sourcing R scripts, e.g.

```{r sourcing, fig.cap = "Example plot created in a scoured R script."}
# you need to use package `here`
source(here::here("code/example-code.R"))
```

For more on the code chunk options/parameters see [R Markdown Ch. 2.6](https://bookdown.org/yihui/rmarkdown/r-code.html).
For example, the `echo = FALSE` parameter was removed in the second code chunk to print of the R code that 
generated Figure \@ref(fig:sourcing).


## Cross referencing

You can cross-reference sections, equations, figures, and tables etc., see [Bookdown Ch. 2.2](https://bookdown.org/yihui/bookdown/markdown-extensions-by-bookdown.html) and [Ch. 2.6](https://bookdown.org/yihui/bookdown/cross-references.html) for details.  
For example, Section \@ref(sec:background) or Figure \@ref(fig:sourcing).


## Citation and References

We strongly recommend to use [Zotero](https://www.zotero.org/) as Reference management software (with [Better Bibtex](https://retorque.re/zotero-better-bibtex/) extension). It is free and open source and has a nice [R Studio integration](https://rstudio.github.io/visual-markdown-editing/citations.html) (see also <https://github.com/crsh/citr> and <https://github.com/paleolimbot/rbbt>).

See [Bookdown Ch. 2.8](https://bookdown.org/yihui/bookdown/citations.html) on how to cite references in R Markdown and
some general background.
